The Oumupo, between music and math

### 2017-05-03 article.tex
Finishes attractor section

\begin{lstlisting}
a = 2.6; x = 0.5; ct = 0;
While[ct <= 30, ct++; x = N[a*x*(1 - x)];
Print[ct, "  ", x]]

0.652  0.59153  0.6282324  0.6072475  0.6200956  0.6125017
0.6170938  0.6143529 0.61600210  0.61501311  0.61560712 
0.61525113  0.61546514  0.61533715  0.61541316 0.61536717
0.61539518  0.61537819  0.61538820  0.61538221  0.61538622
0.61538423 0.61538524  0.61538425  0.61538526  0.61538527
0.61538528  0.61538529  0.61538530 0.61538531  0.615385
\end{lstlisting}
\end{document}

>>>>

\begin{figure}[h]
\begin{lstlisting}
a = 2.6; x = 0.5; ct = 0;
While[ct <= 30, ct++; x = N[a*x*(1 - x)];
Print[ct, "  ", x]]

0.652 0.59153 0.6282324 0.6072475 0.6200956
0.6125017 0.6170938 0.6143529 0.61600210 
0.61501311 0.61560712 0.61525113 0.61546514
0.61533715 0.61541316 0.61536717 0.61539518 
0.61537819 0.61538820 0.61538221 0.61538622
0.61538423 0.61538524 0.61538425 0.61538526
0.61538527 0.61538528 0.61538529 0.61538530
0.61538531 0.615385
\end{lstlisting}
\caption{with $a=2.6$ and $x=0.5$ as a starting point, $x$ becomes 0.65 then 0.59. 0.62. 0.61 etc.
until it stabalizes at 0.615385.}
\end{figure}
\begin{figure}[h]
a = 3.56994; x = 0.5; ct = 0;
While[ct <= 30, ct++; x = N[a*x*(1 - x)];
Print[ct, "  ", x]]

0.8924852 0.3425553 0.8039914 0.5625865
0.8785026 0.3810437 0.8419688 0.4750099
0.89025510 0.34878611 0.81085612 0.54751813
0.88442414 0.36491215 0.82733816 0.50996617 
0.8921318 0.34354919 0.80510320 0.56016621
0.87956222 0.37817323 0.83950124 0.48101125 
0.89119826 0.34615727 0.80799328 0.55384229 
0.88213630 0.37117431 0.833238
\caption{a=3.56994, which is one of Feigenbaum's constants.  The result is
much more chaotic. In spite of the large differences between later
smaller significant figures, the system alternates between two poles -- one
close to 0.8 and the other close to 0.5.  The attractor thus becomes
periodic.}
\end{figure}
\begin{figure}[h]
En d’autres termes, les résultats tendent à s’organiser selon un cycle de quatre valeurs approximatives : tel est l’« attracteur » qui nous intéresse ici.
a = 3.745; x = 0.5; ct = 0;
While[ct <= 100, ct++; x = N[a*x*(1 - x)];
Print[ct, "  ", x]]

0.936252  0.2235243  0.6499864  0.8520045
0.472226  0.933367  0.2329368  0.6691459
0.82910610  0.53062711  0.93273712  0.23495613
0.6731714  0.82394615  0.54324616  0.92924617
0.24622518  0.69506619  0.7937520  0.61309721
0.88834822  0.37145123  0.87436424  0.41139425
0.90684826  0.31635927  0.80995328  0.57646429
0.91435430  0.29327331  0.77620432  0.65054933
0.8513734  0.47388935  0.93369736  0.23184237
0.66695238  0.83186539  0.52379640  0.93412941
0.23043642  0.66412143  0.83537644  0.51502445
0.93540546  0.22628347  0.65567148  0.84549549
0.4892250  0.93581551  0.22494552  0.65292153
0.84867454  0.48095855  0.93489256  0.22795457
0.65908658  0.8414759  0.49957660  0.93624961
0.22352662  0.6499963  0.85199864  0.47223465
0.93336366  0.23292767  0.66912668  0.82912969
0.5305770  0.9327571  0.23491372  0.67308573
0.82405574  0.54298175  0.92933276  0.2459577
0.69454378  0.79451379  0.61141780  0.8897681
0.36733582  0.87033883  0.42262184  0.91382785
0.29490886  0.77872687  0.64530888  0.85717689
0.45848390  0.92979591  0.2444692  0.69169993
0.79862694  0.6022895  0.89707396  0.34578797
0.84718898  0.4848399  0.935388100  0.226337101
0.655782
\caption{This configuration is less table and the numbers obtained are
completely dispersed.  Nevertheless, if one listens to the result in time,
one can hear an emergent logic in a random alteration between five disntinct
values.  In this way, music reveals what a base ten numerical system,
ill-adapted to the representation of dynamic system, often obfuscates.}
\end{figure}

\end{document}
